---
title: "Computer1"
output:
  pdf_document: default
  html_document: default
date: "2023-10-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Importing the data

```{r}
data <- read.table("tobacco.txt", header = TRUE, sep = "\t", row.names = 1)
```

a)  ILL = constant + B\*consumption + error

b)  

```{r}
fit = lm(ILL ~ CONSUMPTION, data = data)
coefficients(fit)
```

The regression coefficient for consumption is B = 0.2291153, which would mean that the weight of consumption is not too high with being ill

c)  

```{r}
r_squared <- summary(fit)$r.squared
r_squared
```

d)  

```{r}
f = summary(fit)$fstatistic

p = pf(f[1],f[2], f[3], lower.tail = FALSE)
p
```

It is statistically significant because p \< 0.01

e)  

```{r}
p_values <- summary(fit)$coefficients[, "Pr(>|t|)"]

p_values[2]


```

It is statistically significant with 1% boundary, the value is equal to the value obtained in part d)

f)  

```{r}
library(ggplot2)

ggplot(data, aes(x = CONSUMPTION, y = ILL)) +
  geom_point() +  # Display data points
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "fit", x = "CONSUMPTION", y = "ILL")

```

g)  A confidence interval means a range of values that is used to estimate an unknown value. For example, a 95% confidence interval means that taking 100 samples, then around 95 of the samples would fall into that range (confidence interval).

h)  

```{r}
conf_interval_95 <- confint(fit, "CONSUMPTION", level = 0.95) 
conf_interval_95
conf_interval_99 <- confint(fit, "CONSUMPTION", level = 0.99)
conf_interval_99
confint(fit, "(Intercept)", level = 0.95)
```

The range of values for ILL has a big range, the data is dispersed, which means there are many suitable intercepts.

i)  

```{r}
# Make matrix X of above formula.
n = nrow(data)
tmp <- as.matrix(data[, c(4)]) 
xmatrix <- cbind(rep(1, n), tmp) 

k <- 2000
alpha <- 0.05
# Number of variables and number of observations.
m <- ncol(xmatrix) 
n <- nrow(xmatrix)
# Create matrix for collecting values of b.
bmatrix <- matrix(NA, nrow = k, ncol = m) 
y <- data$ILL

for (i in 1:(k - 1)) {
  # take random sample of size n (n size of the original sample). 
  ind <- sample(1:n, n, replace = TRUE)
  xtmp <- xmatrix[ind, ]
  ytmp <- y[ind]
  # Calculate bootstrap estimates
  btmp <- solve(t(xtmp) %*% xtmp) %*% t(xtmp) %*% ytmp
  bmatrix[i, ] <- t(btmp) 
}

# Include original estimate
b <- solve(t(xmatrix) %*% xmatrix) %*% t(xmatrix) %*% y 
bmatrix[k, ] <- t(b)

# Calculate confidence interval
qconst <- quantile(bmatrix[, 1], probs = c(0.025, 0.975)) 
qhum <- quantile(bmatrix[, 2], probs = c(0.025, 0.975)) 
qhum
qconst
```

j)  It is simple and easy to implement even on a small data set, nor do you have to make any assumptions about the data, like the normality assumption.
